\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Work Distribution And Sprints}
\author{Litha, Itu, Ngwato, Nyawa}

\begin{document}
\maketitle

\begin{abstract}
\centering draft Software Requirement Specification.
\end{abstract}

\section{Objective}

Getting started on the delivery service, user stories.

\subsection{Content}

\subsection*{User Stories :} What users want as features and abilities on the delivery system.

\subsection*{Admin Stories :} Basic descriptions on how admin will be handled and what
information the Administrator should have.

\section{User Stories}
I want to be able to Create Account online in real time. I want to be
able to update my personal information on the go. I want to be able to
choose my payment option for every transaction. I want to be able to see
my delivery history. I want to see the process of my delivery package. I
want to be able to know how long a package will take before I confirm
an order. I want to be able to cancel a delivery. I want to be able to
communicate with the driver, how far he is, if I cannot see my package. I
want to be able to change my delivery location. If I have a fragile package,
I need to be guaranteed it will arrive in the given condition. I don't want to
be charged too much for delivering small, non-fragile packages. I want to
get a reminder or/and a notification to let me know that my delivery has
arrived. I also want to be able to confirm my delivery. I want to be able
to get a refund if my package is not delivered. I want to be able to have
a quick delivery option. I want guaranteed security, safe package delivery,
safe payment transactions. I want to be able to reset password if i have
forgotten it.

\section{Admin Requirements}
I need to be able to get feedback on delivered packages. I need to know
which packages are on route. I need to know which packages are being
delayed. I want feedback on driver efficiency. I want feedback on user
experience.

\section{Sprint 1: GUI}
Sign in/ Sign up (2hrs) Forgot Password (2hrs) Home Page (4hrs) Delivery
Options(4hrs) Payment Option(2hrs)
\section{Sprint 2: Database}
UML development Database Architecture Relational Database Structure Dummy
users, Drivers, and Admin.
\section{Sprint 3: Back-End}
PHP handling JSON Structures Google MAps API (implementation learn-
ing)
\section{Sprint 4: Payment}
paypal/online banking API Cash Handling(How it will be implemented).
EFT (learn use relative to project)
\section{Sprint 5: App Security}
Login security/ Authentication, Authorization, verification/validation. Time-
outs Resource Allocation Database encryption Payment Security(Digital
keys and Digital signatures)






\end{document}