\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Project Description}
\author{Litha Mguzuli,Ngwato Magabotsa,Itumeleng Malalane,Nyawasedza Marevhula}

\begin{document}
\maketitle

\begin{abstract}
       \emph{Fleet of Delivery and Pick-Up Vehicle Management System}
\end{abstract}

\section{Input}

$\bullet$ Will need pick and drop-off locations, using a mapping system.

$\bullet$ User Login Details

$\bullet$ Driver Interaction (delivery/pick-up confirmation).

$\bullet$ Package Description (Weight, size, fragility etc).

$\bullet$ Package Priority (Classified, High priority, low priority)

\section{Output}

$\bullet$ Generated route for package together with live update of current
location of delivery vehicle(GPS Style).

$\bullet$ Pricing of delivery.

$Description of project$

$\bullet$ Name of Company is \emph{CourierJZ}, respossible for delivery of parcels from beginning point and destination.

$\bullet$ Delivery can be any shape and size, it just has to be stated prior and customers have until 10:00am to book for the current day.

$\bullet$ Driver and customer real time interaction/communication is very vital for efficiency and simple work flow.

$\bullet$ Driver transparency, Generated route for package together with live update of current location
of delivery vehicle(Uber Style).

$\bullet$ Constant confirmation to customer of parcel status (from initial pick up location,en route and delivered).


$Front-end tasks$

$\bullet$ Customer login ins

$\bullet$ Pick up and destination locations,parcel specifications(size, shape , fragility, parcel priority etc)

$\bullet$ Mapping system for the vehicles and route calculations.

$\bullet$ Parcel status(Delivered,on the way,picked up from initial locations etc) and driver status(busy ,free ,en-route etc).

$\bullet$ Driver and Customer chat-box for simplicity and delivery efficiency

$\bullet$ Customer and driver personal details for security.

$\bullet$ Payment options(cash,card,eft etc).

$Back-end tasks$

$\bullet$Customer authentications and authorizations 

$\bullet$Database management and maintenance.

$\bullet$Input validations and verifications. 

\section{Task Description}
\subsection{Nyawasedza Marevhula}:Database architecture, database management and maintenance.

\subsection{Ngwato Magabotsa}: Graphical User Interface,App design flow(how user will navigate through App).

\subsection{Itumeleng Malalane and Litha Mguzuli}: Connecting front end with back end ,User inputs, verification of input with database, validation handling, Using a map or/and mapping API.
\end{document}